Distributed Nonlinear Control Design using Separable Control Contraction Metrics

### 2017-06-01 R0V0.tex
Merge Ian's change in the example and conclusion

\mypara Based on these paragraphs, the question of how restrictive is the requirement of $M$ to have a block-diagonal structure remains open. As mentioned before, the main advantage to look for control-contraction metric with a diagonal structure is that it allows to exploit sparsity to design controllers for large scale systems. This is illustrated in the next section.

@@

\mypara In terms of semidefinite programming, employing control-contraction metrics allows one to formulate the search for the controller as a convex optimization problem. Although this is one of its main advantages over the search of control-Lyapunov functions, it cannot handle systems with a large number of states, in general.

>>>>

\mypara Based on these paragraphs, the question of how restrictive is the requirement of $M$ to have a block-diagonal structure remains open. As mentioned before, the main advantage to look for control contraction metric with a diagonal structure is that it allows to exploit sparsity to design controllers for large scale systems. This is illustrated in the next section.

@@

\mypara In terms of semidefinite programming, employing control contraction metrics allows one to formulate the search for the controller as a convex optimization problem. Although this is one of its main advantages over the search of control-Lyapunov functions, it cannot handle systems with a large number of states, in general.
